\thetitle

### 2021-06-27 writing/rational-transient.tex
Fix the transient first/last definition

\begin{quote}
\it A \emph{Transient-first blame trail}{\lrdef}\emph{Transient-last blame trail} is a sequence of scenarios
$\conf_0,...\conf_n$ of $\system$ where for all $0 \leq i \leq n - 1$,
$\conf_i \subset \conf_{i+1}$ and
\[ \conf_{i+1} \setminus \conf_i = %
\left\{ %
\begin{tabular}{ll} %
$\{\first{\mblame{\system, \conf_i}}\}$  & if $\conf_i$ produces blame \\ %
$\{\exception{\system, \conf_i}\}$     & otherwise \\ %
\end{tabular} \right. %
\]
where $\first{\mblame{\system, \conf}}${\lrdef}$\last{\mblame{\system, \conf}}$ is the
first{\lrdef}last module, respectively,  that Transient adds to the blame sequence for $\conf$.
\end{quote}

>>>>

\begin{quote}
\it A \emph{Transient-first blame trail}{\lrdef}\emph{Transient-last blame trail} is a sequence of scenarios
$\conf_0,...\conf_n$ of $\system$ where for all $0 \leq i \leq n - 1$,
$\conf_i \subset \conf_{i+1}$ and
\[ \conf_{i+1} \setminus \conf_i = %
\left\{ %
\begin{tabular}{ll} %
$\{\first{\mblame{\system, \conf_i}}$ \lrdef $\last{\mblame{\system, \conf_i}}\}$  & if $\conf_i$ produces blame \\ %
$\{\exception{\system, \conf_i}\}$     & otherwise \\ %
\end{tabular} \right. %
\]
where $\first{\mblame{\system, \conf}}${\lrdef}$\last{\mblame{\system, \conf}}$ is the
first{\lrdef}last module, respectively,  that Transient adds to the blame sequence for $\conf$.
\end{quote}
